\LARGE \bf Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty [v-14 09-30-2014]

### 2014-10-02 paper.tex
changes michael

\author{Michael Laskey$^1$, Zoe McCarthy$^1$, Jeff Mahler$^1$, Florian T. Pokorny$^3$, Sachin Patil$^1$,\\ Jur Van Den Berg$^4$,  Danica Kragic$^3$, Pieter Abbeel$^1$, Ken Goldberg$^2$% <-this % stops a space
\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\tt\small \{mdlaskey, zmccarthy, jmahler, sachinpatil, pabbeel\}@berkeley.edu}}%
\thanks{$^2$Department of Industrial Engineering and Operations Research and Department of Electrical Engineering and Computer Sciences; {\tt\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
\thanks{$^3$Computer Vision and Active Perception Lab, Centre for Autonomous Systems, School of Computer Science and Communication, KTH Royal Institute of Technology, Stockholm, Sweden {\tt\small \{fpokorny, dani\}@kth.se}}%
\thanks{$^4$Google; Amphitheatre Parkway, Mountain View, CA 94043, USA {\tt\small jurvandenberg@gmail.com}}%
}

@@

\subsection{Gaussian Process (GP) Background} \todo{massive trim down}
GPs provide an infinite dimensional analogue of Multivariate
Gaussian Distributions which allow us to model distributions over
functions. Gaussian processes (GPs) are widely used in machine learning as a nonparametric regression method for estimating continuous functions from sparse and noisy data \cite{rasmussen2010gaussian}.
In a GP, a training set consists of input vectors $\mX = \{\bx_1, \ldots, \bx_n\}$, $\bx_i \in \mathbb{R}^d$, and corresponding observations $\by = \{y_1, \ldots, y_n\}$. The observations are assumed to be noisy measurements from the unknown target function $f$:
\begin{equation}
y_i = f(\bx_i) + \epsilon,
\end{equation}
where $\epsilon \sim \mN(0,\sigma^2)$ is Gaussian noise in the observations.
A zero-mean Gaussian process is completely specified by a covariance function $k(\cdot,\cdot)$, also referred to as a kernel.
Given the training data $\mD = \{\mX, \by\}$ and covariance function $k(\cdot,\cdot)$, the posterior density $p(f_*|\bx_*,\mD)$ at a test point $\bx_{*}$ is shown to be \cite{rasmussen2010gaussian}:
\begin{align*}
	p(f_*|\bx_*,\mD) &\sim \mN\big(\mu(\bx_*), \Sigma(\bx_*)\big) \\
	\mu(\bx_*) &= k(\mX,\bx_*)^{\intercal}(K + \sigma^2I)^{-1}\by \\
	\Sigma(\bx_*) &= k(\bx_*,\bx_*)-k(\mX,\bx_*)^{\intercal}(K+\sigma^2I)^{-1}k(\mX,\bx_*)\big) 
\end{align*}
where $K \in \mathbb{R}^{n \times n}$ is a matrix with entries $K_{ij} = k(\bx_i,\bx_j)$ and $k(\mX,\bx_*) = [k(\bx_1,\bx_*),\ldots,k(\bx_n,\bx_*)]^{\intercal}$. 
This derivation can also be used to predict the mean and variance of the function gradient by extending the kernel matrices using the identities \cite{solak2003derivative}:

\vspace{-2ex}
\begin{align}
	\text{cov}\left(f(\bx_i), f(\bx_j) \right) &=  k(\bx_i, \bx_j) \\
	\text{cov}\left(\frac{\partial f (\bx_i)}{\partial x_k}, f(\bx_j) \right) &= \frac{\partial}{\partial x_k} k(\bx_i, \bx_j) \label{eq:mean_gradient}\\
	\text{cov}\left(\frac{\partial f (\bx_i)}{\partial x_k}, \frac{\partial f (\bx_j)}{\partial x_l} \right) &= \frac{\partial^2}{\partial x_k \partial x_l} k(\bx_i, \bx_j)\label{eq:cov_gradient}
\end{align}

\begin{figure}[ht!]
\centering
\includegraphics[width = 8.5cm, height = 14cm ]{figures/Slide03.jpg}
\caption{\footnotesize Six example objects illustrating transparency, specularity, sensor noise that illustrate the need for shape uncertainty: (from top to bottom) tape, squirt bottle, stapler, loofa, marker, water bottle. Displayed from right to left are the HD color image, a point cloud observation from a Primesense Carmine, GPIS visualization technique from \cite{jeffs}, the nominal shape on a $25 \times 25$ grid.  }
\vspace*{-10pt}
\label{fig:GPIS_TSDF}
\end{figure}
%\section{Related Work}

For our kernel choice we decided to use the square exponential kernel, a major reason for this was its differentiability. Other kernels relevant to GPIS are the thin-plate splines kernel and the Matern kernel \cite{williams2007}.

@@

\section{Evaluating a Grasp}
 In order to solve our problem definition, we must evaluate $E(Q(\Gamma))$ for a given grasp plan $\Gamma$. We will first discuss which grasp metric $Q$ we chose and then proceed into evaluating the expectation $E$ efficiently.

>>>>

\author{Michael Laskey, Zoe McCarthy, Jeff Mahler, Florian T. Pokorny, Sachin Patil,\\ Jur Van Den Berg,  Danica Kragic, Pieter Abbeel, and Ken Goldberg}% <-this % stops a space

@@

\section{Evaluating a Grasp}
 In order to solve our problem definition, we must evaluate $E(Q(\Gamma))$ for a given grasp plan $\Gamma$. We will first discuss how the GPIS is constructed, then which grasp metric $Q$ we chose and lastly proceed into evaluating the expectation $E$ efficiently.

\subsection{Gaussian Process (GP) Background}
Given the training data $\mD = \{\mX, \by\}$ and covariance function $k(\cdot,\cdot)$, the posterior density $p(sd_*|\bx_*,\mD)$ at a test point $\bx_{*}$ is shown to be \cite{rasmussen2010gaussian}:
\begin{align*}
	p(sd_*|\bx_*,\mD) &\sim \mN\big(\mu(\bx_*), \Sigma(\bx_*)\big) \\
	\mu(\bx_*) &= k(\mX,\bx_*)^{\intercal}(K + \sigma^2I)^{-1}\by \\
	\Sigma(\bx_*) &= k(\bx_*,\bx_*)-k(\mX,\bx_*)^{\intercal}(K+\sigma^2I)^{-1}k(\mX,\bx_*)\big) 
\end{align*}
where $K \in \mathbb{R}^{n \times n}$ is a matrix with entries $K_{ij} = k(\bx_i,\bx_j)$ and $k(\mX,\bx_*) = [k(\bx_1,\bx_*),\ldots,k(\bx_n,\bx_*)]^{\intercal}$. 
This derivation can also be used to predict the mean and variance of the function gradient by extending the kernel matrices using the identities \cite{solak2003derivative}:

\vspace{-2ex}
\begin{align}
	\text{cov}\left(sd(\bx_i), sd(\bx_j) \right) &=  k(\bx_i, \bx_j) \\
	\text{cov}\left(\frac{\partial sd (\bx_i)}{\partial x_k}, sd(\bx_j) \right) &= \frac{\partial}{\partial x_k} k(\bx_i, \bx_j) \label{eq:mean_gradient}\\
	\text{cov}\left(\frac{\partial sd (\bx_i)}{\partial x_k}, \frac{\partial sd (\bx_j)}{\partial x_l} \right) &= \frac{\partial^2}{\partial x_k \partial x_l} k(\bx_i, \bx_j)\label{eq:cov_gradient}
\end{align}

For our kernel choice we decided to use the square exponential kernel, similar to \cite{dragiev2011}. Other kernels relevant to GPIS are the thin-plate splines kernel and the Matern kernel \cite{williams2007}.

@@
